\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-09 trunk/results.tex
updates

Our early work focused on observing and sampling within Intermediate
Nephaloid Layers (INLs) \footnote{INLs are fluid sheets of suspended
  particulate matter that originate from the sea floor
  \cite{mcphee-shaw2006}} \cite{ryan10}. The location and scale of
INLs in the water column, which depend upon seasonal and episodic
variability, are not predictable. In turn, they can be identified by
their high turbidity and low chlorophyll fluorescence. Initial
objectives focused on ways to enhance survey results by ensuring as
large a coverage as possible so that INL fields were observed at
tighter spaced transects and when no INL is detected, then transect
spacing in the lawn mower can be incrementally increased. Follow on
work directly targeted sample acquisition within INLs which are often
sparse, patchy in large horizontal scales (in Kms) and small vertical
scales (in meters). Fig. \ref{inl} shows one example from an AUV
transect from 2005. The intent of both observation and sample
acquisition was to interrupt the nominal plan-execution cycle and
inject an action to alter and re-factor the plan dynamically; in one
instance altering the navigation, the other in actuating a sampler.

@@

\begin{figure*}
\centering
\subfloat[]{\label{fig:odss-mtg}\includegraphics[width=0.3\textwidth]{figs/october-canon-meeting.png}}
\subfloat[]{\label{fig:odss-virtual}\includegraphics[width=0.33\textwidth]{figs/virtual-drifter-tool.png}}
\subfloat[]{\label{fig:odss-ipad}\includegraphics[width=0.3\textwidth]{figs/photo-ipad-2.jpg}}
\caption{\small Fig. \ref{fig:odss-mtg} shows a 2010 \can meeting with the
  \od in use while Fig. \ref{fig:odss-ipad} shows its use on a portable
  device.}
xf\label{fig:odss2}
\end{figure*}

>>>>

Our early work focused on observing and sampling within Intermediate
Nephaloid Layers (INLs) \footnote{INLs are fluid sheets of suspended
  particulate matter that originate from the sea floor
  \cite{mcphee-shaw2006}} \cite{ryan10}. The location and scale of
INLs in the water column, which depend upon seasonal and episodic
variability, are not predictable. In turn, they can be identified by
their high turbidity and low chlorophyll fluorescence. Initial
objectives focused on ways to enhance survey results by ensuring as
large a coverage as possible so that INL fields were observed at
tighter spaced transects and when no INL is detected, then transect
spacing in the lawn mower can be incrementally increased. Follow on
work directly targeted sample acquisition within INLs which are often
sparse, patchy in large horizontal scales (in Kms) and small vertical
scales (in meters). Fig. \ref{fig:inl} shows one example from an AUV
transect from 2005. The intent of both observation and sample
acquisition was to interrupt the nominal plan-execution cycle and
inject an action to alter and re-factor the plan dynamically; in one
instance altering the navigation, the other in actuating a sampler.

@@

\begin{figure*}
\centering
\subfloat[]{\label{fig:odss-mtg}\includegraphics[width=0.3\textwidth]{figs/october-canon-meeting.png}}
\subfloat[]{\label{fig:odss-virtual}\includegraphics[width=0.33\textwidth]{figs/virtual-drifter-tool.png}}
\subfloat[]{\label{fig:odss-ipad}\includegraphics[width=0.3\textwidth]{figs/photo-ipad-2.jpg}}
\caption{\small Fig. \ref{fig:odss-mtg} shows a 2010 \can meeting with
  the \od in use. Fig. \ref{fig:odss-virtual} shows a drifter tracking
  tool used during \can planning; it used a physical model of advected
  surface currents from \texttt{CeNCOOS} \cite{cencoos} to plan AUV
  deployments. Fig. \ref{fig:odss-ipad} shows \od use on a portable
  iPad device.}
\label{fig:odss2}
\end{figure*}
